---
title: "p8105_hw1_kd2524-for-Jeff"
author: "Katherine Dimitropoulou_UNI_kd2524"
date: "9/20/2019"
output: github_document
---

###Problem 1

##Step 1_Create a data frame comprised of:
#a random sample of size 8 from a standard Normal #distribution
#a logical vector indicating whether elements of the sample are greater than 0
#a character vector of length 8
#a factor vector of length 8, with 3 different factor “levels”

##Then compute the means for the variables in the dataset

#Code Chunk

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

library(tidyverse)
set.seed(1)
```
```{r, Hw1Probl1_df}
Hw1Probl1_df = tibble (
  norm_set = rnorm(8),
  norm_pos = norm_set > 0,
  Question_char = c("Q1", "Q2", "Q3", "Q4", "Q5", "Q6", "Q7", "Q8"),
  Response_factor = factor(c("Agree", "Neutral", "Disagree", "Disagree", "Agree", "Neutral", "Neutral", "Agree"))
)
```
#Mean of numeric variable 
mean(pull(Hw1Probl1_df, norm_set))
#Mean of logical variable 
mean(pull(Hw1Probl1_df, norm_pos))
#Mean of character variable 
mean(pull(Hw1Probl1_df, Question_char))
#Mean of factor variable 
mean(pull(Hw1Probl1_df, Response_factor))

#There is no mean for the character and factor variables because they are not numeric or logical.

##Step 2
#Use as.numeric function on the variables from Hw1Probl1_df. 
#Code Chunk
```{r, eval = FALSE}
Hw1Probl1_num_df = tibble(
  norm_set = rnorm(8),
  norm_pos = as.numeric(norm_set > 0),
  Question_char = as.numeric(c("Q1", "Q2", "Q3", "Q4", "Q5", "Q6", "Q7","Q8")),
  Response_factor = as.numeric(factor(c("Agree", "Neutral", "Disagree", "Disagree", "Agree", "Neutral", "Neutral", "Agree")))
)
```
# Step 3 Create a code chunk for the following conversions:
#conversion of  the logical vector to numeric, and multiply the random sample by the result
#conversion the logical vector to a factor, and multiply the random sample by the result
#conversion the logical vector to a factor and then convert the result to numeric, and multiply the random sample by the result

#Code Chunk
```{r, eval = FALSE}
Hw1Probl1_convert_df = tibble(
  norm_set = rnorm(8),
  norm_pos_num = as.numeric(norm_set > 0),
  Product1 = norm_set*norm_pos_num,
  norm_pos_factor = as.factor(norm_set > 0),
  Product2 = norm_set*norm_pos_factor,
  norm_pos_factor_num = as.numeric(as.factor(norm_set > 0)),
  Product3 = norm_set*norm_pos_factor_num
)
```

###Problem 2

##Step 1
#Create a data frame comprised of the following:  
#x: a random sample of size 500 from a standard Normal distribution  
# y: a random sample of size 500 from a standard Normal distribution  
# A logical vector indicating whether x + y > 1  
#A numeric vector created by coercing the above logical vector  
#A factor vector created by coercing the above logical vector  
```{r, Hw1Probl2}
Hw1Probl2_df = tibble(
  x = rnorm(500),
  y = rnorm(500),
  log_sum_xy1 = x + y > 1,
  Log_sum_xy1_num = as.numeric(x + y > 1),
  log_sum_xy1_factor = as.factor(Log_sum_xy1_num)
)
```
## Step 2
#Write a short description of your vector using inline R code, including: 
#the size of the dataset (using nrow and ncol) 
 nrow(Hw1Probl2_df)
 ncol(Hw1Probl2_df)
#the mean, median, and standard deviation of x 
 mean(pull(Hw1Probl2_df, x))
 median(pull(Hw1Probl2_df, x))
 sd(pull(Hw1Probl2_df, x))
#the proportion of cases for which x + y > 1
#Because it is a binary var we can use the mean function for proportion, 
 mean(pull(Hw1Probl2_df, Log_sum_xy1_num))
# NOTE: We can also use the following for computation of proportions if the variable is not binary #sum(pull(Hw1Probl2_df, Log_sum_xy1_num)) /length(pull(Hw1Probl2_df, Log_sum_xy1_num))`.
 

 
#Scatter plot adding color using logical variable:
```{r yx_scat1}
ggplot(Hw1Probl2_df, aes(x = x, y = y, color = log_sum_xy1)) + geom_point()
```
 
#Scatter plot adding color using numeric variable:
```{r yx_scat2}
ggplot(Hw1Probl2_df, aes(x = x, y = y, color = Log_sum_xy1_num)) + geom_point()
```
 
#Scatter plot adding color using factor variable:
```{r yx_scat3}
ggplot(Hw1Probl2_df, aes(x = x, y = y, color = log_sum_xy1_factor)) + geom_point()
```


